Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-07-30 writing/nips_submission/response/EML_response.tex
Some tweaks and mini imagenet results

\textbf{The insight of our paper is that learning a meta-mapping over polynomials is exactly analogous to learning a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of input polynomials and output polynomials for the meta-mapping that operates over polynomials (e.g. multiplying by 2). Specifically, a set of polynomials are embedded as above, by passing examples of them through the meta network to compute a function embedding for each one. We then take a set of pairs of (embedded input polynomial, embedded target polynomial), and pass them through the \textbf{exact same meta network} $\mathcal{M}$ to produce an embedding for the function that transforms one polynomial into another. Just as above, we pass this function embedding through the same hyper network $\mathcal{H}$ to parameterize a function $F$ which attempts to multiply polynomials by 2. We can then pass a probe polynomial through $F$ to produce a predicted output. The only differences from the basic case are: 1) where the inputs and targets come from 2) how the loss or evaluation is computed from the predictions. For basic training, we used an appropriate loss in the output space for each task, in meta training, we used an $\ell^2$ between the predicted task embedding, and the embedding of the target task. One of the main algorithmic insights of our work is that this produces $z^{func}$ embeddings which approximate the desired meta-mapping well, even for meta-mappings not included in training (see fig. 3). To evaluate meta-mapping performance, we actually computed the performance of the predicted output embedding at computing the target polynomial. For example, if the meta-mapping was ``multiply by 2'' and the probe input was the function embedding of $x + 2$, we would evaluate how closely the predicted output polynomial matched $2x + 4$ by feeding the predicted function embedding to the hyper network to parameterize a function, feeding input values to this function, and then measuring its predicted outputs against the real values of $2x+4$ at those inputs. We hope this clarifies our approach, and why it is fundamentally different from prior work. All three reviewers highlighted the novelty of considering transformations over tasks. That is the conceptual contribution of our paper, and the algorithmic contribution is to show an approach for solving this challenge. Notably, because we use the same networks for both basic tasks and meta-mappings, our approach is parsimonious --- it does not require adding any new parameters to the model. (We show in Appendix D.1 that this actually performs better than having separate meta and hyper networks for basic tasks and meta-mappings.) While other meta-learning approaches could potentially be adapted to do meta-mappings, it is unclear that they could be adapted so parsimoniously, or perform well. However, we think exploring alternate approaches, or combining algorithms like MAML with architectures like ours, provide exciting future directions. For now, we are revising the main text to clarify our message. \par 

@@

\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a 50-layer ResNet as the input encoder, we achieved test accuracy of 58.9\% on 5-shot, 5-way classification, competitive with e.g. MAML. We expect that given more than a few days to tune hyperparameters and architecture we could do much better. \par

@@

\textbf{Language \& continual learning:} We wanted to include language because it provides a simpler way to cue meta-mappings. Specifically, we used the language embedding as input to $H$ instead of using examples. For continual learning, while approaches like LEO generate (and even optimize) task embeddings, we are not aware of prior work that describes the continual learning approach of optimizing only the cached embeddings. Approaches like EWC double the parameter count by adding an ``importance'' parameter for each model parameter. For modern models with up to billions of parameters, caching a relatively low-dimensional task embedding instead would be advantageous even up to millions of tasks. In revising the paper, we will emphasize the main points before discussing these extensions. 

>>>>

\textbf{The insight of our paper is that learning a meta-mapping over polynomials is exactly analogous to learning a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of input polynomials and output polynomials for the meta-mapping that operates over polynomials (e.g. multiplying by 2). Specifically, a set of polynomials are embedded as above, by passing examples of them through the meta network to compute a function embedding for each one. We then take a set of pairs of (embedded input polynomial, embedded target polynomial), and pass them through the \textbf{exact same meta network} $\mathcal{M}$ to produce an embedding for the function that transforms one polynomial into another. Just as above, we pass this function embedding through the same hyper network $\mathcal{H}$ to parameterize a function $F$ which attempts to multiply polynomials by 2. We can then pass a probe polynomial through $F$ to produce a predicted output. The only differences from the basic case are: 1) where the inputs and targets come from 2) how the loss or evaluation is computed from the predictions. For basic training, we used an appropriate loss in the output space for each task; in meta training, we used an $\ell^2$ between the predicted task embedding and the embedding of the target task. One of the main algorithmic insights of our work is that this produces $z^{func}$ embeddings which approximate the desired meta-mapping well, even for meta-mappings not included in training (see fig. 3). To evaluate meta-mapping performance, we actually computed the performance of the predicted output embedding at computing the target polynomial. For example, if the meta-mapping was ``multiply by 2'' and the probe input was the function embedding of $x + 2$, we would evaluate how closely the predicted output polynomial matched $2x + 4$, by feeding the predicted function embedding to the hyper network to parameterize a function, feeding input values to this function, and then measuring its predicted outputs against the real values of $2x+4$ at those inputs. We hope this clarifies our approach, and why it is fundamentally different from prior work. All three reviewers highlighted the novelty of considering transformations over tasks. That is the conceptual contribution of our paper, and the algorithmic contribution is to show an approach for solving this challenge. Notably, because we use the same networks for both basic tasks and meta-mappings, our approach is parsimonious --- it does not require adding any new parameters to the model. (We show in Appendix D.1 that this actually performs better than having separate meta and hyper networks for basic tasks and meta-mappings.) While other meta-learning approaches could potentially be adapted to do meta-mappings, it is unclear that they could be adapted so parsimoniously, or perform well. However, we think exploring alternate approaches, or combining algorithms like MAML with architectures like ours, provide exciting future directions. For now, we are revising the main text to clarify our message. \par 

@@

\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet-50 as the input encoder, we achieved test accuracy of 61.0\% on 5-shot, 5-way classification, competitive with e.g. MAML. We expect that with more than a few days to tune hyperparameters and train larger models we could do much better. \par

@@

\textbf{Language \& continual learning:} In the revised paper we will emphasize the main points before discussing these extensions. We wanted to include language because it provides a simpler way to cue meta-mappings. Specifically, we used the language embedding as input to $\mathcal{H}$ instead of using examples via $\mathcal{M}$. For continual learning, while approaches like LEO generate (and even optimize) task embeddings, we are not aware of prior work that describes the continual learning approach of optimizing only the cached embeddings. Approaches like EWC double the parameter count by adding an ``importance'' parameter for each model parameter. For modern models with up to billions of parameters, caching a relatively low-dimensional task embedding instead could require less memory even up to millions of tasks. 
